Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-07-27 writing/DraftExposurePaper/DraftExposurePaper.Rmd
Frances precip comparison

```{r}

>>>>

```{r}
#frances_gauge <- read.csv("/Users/joshuaferreri/Documents/NWR_frances_gauge.csv", header = TRUE)
#save(frances_gauge, file = "writing/DraftExposurePaper/frances_gauge.RData")
#load("~/Documents/hurricaneexposure/writing/DraftExposurePaper/frances_gauge.RData")
frances_gauge$precip_mm <- convert_precip(frances_gauge$precip_in, "inches", "mm")
frances_nldas <- county_rain(counties = unique(frances_gauge$fips),
                             start_year = 2004, end_year = 2004,
                             rain_limit = 0, dist_limit = 1500,
                             days_included = c(-2, -1, 0, 1))
frances_nldas <- frances_nldas %>%
        filter(storm_id == "Frances-2004")
frances_gauge$fips <- as.character(frances_gauge$fips)
compare_rain <- right_join(frances_nldas, frances_gauge, by = "fips")
b <- ggplot(compare_rain, aes(x = tot_precip, y = precip_mm,
                              color = fips)) +
        geom_point() + 
        theme_bw()
b
```

```{r echo = FALSE, fig.width = 5.5, fig.height = 4}
compare_rain %>% group_by(fips) %>%
        summarize(ave_rain_mm = mean(precip_mm),
                  ave_tot_precip = mean(tot_precip),
                  n = n(),
                  within_500_km = first(storm_dist) <= 500) %>%
        ggplot(aes(x = ave_tot_precip, y = ave_rain_mm, 
                   size = n, color = within_500_km)) + 
        geom_hline(yintercept = 75, color = "gray") + 
        geom_vline(xintercept = 75, color = "gray") + 
        geom_point(alpha = 0.5) + 
        theme_bw() +
        xlim(c(10, 225)) + ylim(c(10, 225)) + 
        geom_abline(intercept = 0, slope = 1) + 
        xlab("Rainfall based on NLDAS-2 data (mm)") + 
        ylab("Rainfall reported in Monthly \nWeather Report (mm)") + 
        scale_color_manual(values = c("blue", "black"), guide = "none") 
```
